### 2021-04-27 abstract.tex
Resolve overfull lines
by small changes.

State-of-the-art superposition-based theorem provers for \acrlong{fol}
rely on \glspl{sot} to constrain the applicability of inference rules,
which in turn shapes the ensuing search space.
The popular Knuth-Bendix simplification ordering is parameterized by 
a \emph{symbol precedence}---a permutation of the predicate and function symbols
of the input problem's signature.
Thus, the choice of a precedence has an indirect yet often substantial impact
on the amount of work required to successfully complete a proof search.

>>>>

The state-of-the-art superposition-based theorem provers for first order logic
rely on \glspl{sot} to constrain the applicability of inference rules,
which in turn shapes the ensuing search space.
The popular Knuth-Bendix simplification ordering is parameterized by 
\emph{symbol precedence}---a permutation of the predicate and function symbols
of the input problem's signature.
Thus, the choice of precedence has an indirect yet often substantial impact
on the amount of work required to complete a proof search successfully.

### 2021-04-27 evaluation.tex
Resolve overfull lines
by small changes.

Adaptive sampling balanced
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator kept track of the number of times the problem has been tried $n_P$,
and the number of examples generated from that problem $s_P$.
The ratio $\frac{s_P}{n_P}$ corresponded to the average reward of problem $P$ observed so far.
The problems were sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
% FB: The parallelizing relaxation is not described in Auer2002. We have designed it ourselves.

>>>>

We employed adaptive sampling to balance
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator kept track of the number of times the problem has been tried $n_P$,
and the number of examples generated from that problem $s_P$.
The ratio $\frac{s_P}{n_P}$ corresponded to the average reward of problem $P$ observed so far.
The problems were sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
% FB: The parallelizing relaxation is not described in Auer2002. We have designed it ourselves.

### 2021-04-27 main.tex
Correct formatting of clever references
Always capitalize.
Use "Sect." and "Sects." unless beginning a sentence.
Use package 'times' to shrink the text to less than 15 pages
Use a more parsimonous font.
Resolve overfull lines
by small changes.

\usepackage{cleveref}

@@

@@

This work was supported by
the Czech Science Foundation project no.~20-06390Y (JUNIOR grant),
the project RICAIP no.~857306 under the EU-H2020 programme,
and
the Grant Agency of the Czech Technical University in Prague, grant
no.~SGS20/215/OHK3/3T/37.

>>>>

\usepackage[capitalise]{cleveref}
\crefname{section}{Sect.}{Sects.}
\Crefname{section}{Section}{Sections}

@@

\usepackage{times}

@@

This work was generously supported by
the Czech Science Foundation project no.~20-06390Y (JUNIOR grant),
the project RICAIP no.~857306 under the EU-H2020 programme,
and
the Grant Agency of the Czech Technical University in Prague, grant
no.~SGS20/215/OHK3/3T/37.
